---
title: "March 2022 host and holobiont protein analysis"
author: "HM Putnam, AS Huffmyer"
edited by: "DM Becker-Polinski"
date: "20230808"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# load packages
library(tidyverse)
library(broom)
library(plotrix)
library(patchwork)
library(performance)
library(ggpubr)
library(rstatix)
library(see)
library(ggpmisc)

```

# Calculate each plate with respect to its standard curve
# 20220808host 20220810holo 20230614host, 20230614holo

# 20220808 Host
# Import data 
```{r}
# Load data
prot_data <- read.csv("data/protein/20220808_May_BCA_host_data_prot.csv")         # List all files in directory
platemap <- read.csv("data/protein/20220808_May_BCA_host_platemap_prot.csv")       # List platemap files
df_host <- right_join(platemap, prot_data, by="Well") # Merge platemap and data for each plate

# Plot standard curve
# Create standard curve following kit instructions
standards_host <- tribble(
  ~std, ~BSA_ug.mL,
  "A",        2000,
  "B",        1500,
  "C",        1000,
  "D",         750,
  "E",         500,
  "F",         250,
  "G",         125,
  "H",          25,
  "I",           0
)

std_curve_host <- df_host %>%
  filter(grepl("Standard", fragment_ID)) %>% #filter standards
  select(Well, fragment_ID, abs562 = "abs562") %>% #select columns
  rename(std = fragment_ID) %>% #name id
  mutate(std = str_sub(std, 9, 9)) %>% #remove the word standard
  mutate(abs562.adj = abs562 - abs562[std == "I"]) %>%       # subtract blank absorbance value from all
  left_join(standards_host) #join with standard concentrations above

#Calculate the calibration curve
mod_host <- lm(BSA_ug.mL ~ abs562, data = std_curve_host) #fit linear model
fitted_host <- mod_host %>% broom::augment() #extract the model fitted data
summary(mod_host) #report the model fit

# Plot standard curve with line fit
std_curve_plot_host <- std_curve_host %>%
  ggplot(aes(x = abs562, y = BSA_ug.mL)) + #plot x y
  geom_point(color = "red", size = 3)+ # color standards
  geom_line(data = fitted_host, aes(x = abs562, y = .fitted)) + #add line fit
  stat_poly_eq(use_label(c("eq", "R2")),rr.digits = 4) + #show line fit equation and R2
  labs(title = "BSA Protein Standard curve") #label plot
std_curve_plot_host #view plot

# Calculate protein concentration for all samples using standard curve
prot_host <- df_host %>%
  filter(!grepl("Standard", fragment_ID, Timepoint)) %>%  # Get just samples (not standards)
  select(Well, fragment_ID, Timepoint, abs562) %>%        # Select only needed columns
  filter(!is.na(fragment_ID)) %>%                         # Filter out empty wells
  filter(fragment_ID != "BK") %>%                         # Filter out blank wells
  mutate(prot_ug.mL = map_dbl(abs562, ~ predict(mod_host, newdata = data.frame(abs562 = .))))    # Use standard curve to convert absorbance to protein

prot_host <- na.omit(prot_host) #remove rows with NA
prot_host <- prot_host %>% filter(prot_ug.mL > 0) #remove any rows with impossible values

#plot samples projected onto standards to check that they fall in range of the standards
std_curve_plot_host + 
  geom_point(data = prot_host, aes(x = abs562, y = prot_ug.mL), pch = "X", cex = 5, alpha = 0.3) + #add points
  labs(title = "All samples projected on standard curve") #label plot

#start dataframe to add all values to after plate specific calculations
tpc.host.protein <- prot_host

```

# 20220614 Host
# Import data 
```{r}
# Load data
prot_data <- read.csv("data/protein/20230614_Dec_BCA_host_data_prot.csv")         # List all files in directory
platemap <- read.csv("data/protein/20230614_Dec_BCA_host_platemap_prot.csv")       # List platemap files
df_host <- right_join(platemap, prot_data, by="Well") # Merge platemap and data for each plate

# Plot standard curve
# Create standard curve following kit instructions
standards_host <- tribble(
  ~std, ~BSA_ug.mL,
  "A",        2000,
  "B",        1500,
  "C",        1000,
  "D",         750,
  "E",         500,
  "F",         250,
  "G",         125,
  "H",          25,
  "I",           0
)

std_curve_host <- df_host %>%
  filter(grepl("Standard", fragment_ID)) %>% #filter standards
  select(Well, fragment_ID, abs562 = "abs562") %>% #select columns
  rename(std = fragment_ID) %>% #name id
  mutate(std = str_sub(std, 9, 9)) %>% #remove the word standard
  mutate(abs562.adj = abs562 - abs562[std == "I"]) %>%       # subtract blank absorbance value from all
  left_join(standards_host) #join with standard concentrations above

#Calculate the calibration curve
mod_host <- lm(BSA_ug.mL ~ abs562, data = std_curve_host) #fit linear model
fitted_host <- mod_host %>% broom::augment() #extract the model fitted data
summary(mod_host) #report the model fit

# Plot standard curve with line fit
std_curve_plot_host <- std_curve_host %>%
  ggplot(aes(x = abs562, y = BSA_ug.mL)) + #plot x y
  geom_point(color = "red", size = 3)+ # color standards
  geom_line(data = fitted_host, aes(x = abs562, y = .fitted)) + #add line fit
  stat_poly_eq(use_label(c("eq", "R2")),rr.digits = 4) + #show line fit equation and R2
  labs(title = "BSA Protein Standard curve") #label plot
std_curve_plot_host #view plot

# Calculate protein concentration for all samples using standard curve
prot_host <- df_host %>%
  filter(!grepl("Standard", fragment_ID, Timepoint)) %>%  # Get just samples (not standards)
  select(Well, fragment_ID, Timepoint, abs562) %>%        # Select only needed columns
  filter(!is.na(fragment_ID)) %>%                         # Filter out empty wells
  filter(fragment_ID != "BK") %>%                         # Filter out blank wells
  mutate(prot_ug.mL = map_dbl(abs562, ~ predict(mod_host, newdata = data.frame(abs562 = .))))    # Use standard curve to convert absorbance to protein

prot_host <- na.omit(prot_host) #remove rows with NA
prot_host <- prot_host %>% filter(prot_ug.mL > 0) #remove any rows with impossible values

#plot samples projected onto standards to check that they fall in range of the standards
std_curve_plot_host + 
  geom_point(data = prot_host, aes(x = abs562, y = prot_ug.mL), pch = "X", cex = 5, alpha = 0.3) + #add points
  labs(title = "All samples projected on standard curve") #label plot

#start dataframe to add all values to after plate specific calculations
tpc.host.protein <- rbind(tpc.host.protein, prot_host)

```


# Normalize Host protein to surface area
```{r}

tpc.host.protein$ID <- paste0(tpc.host.protein$fragment_ID, tpc.host.protein$Timepoint)

# Load Surface area data
May_sa <- read.csv("data/May_TPC_Phys_surface.area.calc.csv")

May_homog.vol <- read_csv("data/May_TPC_Phys_homogenate_vols.csv") 

# Load Surface area data
Dec_sa <- read.csv("data/Dec_TPC_Phys_surface.area.calc.csv")

Dec_homog.vol <- read_csv("data/Dec_TPC_Phys_homogenate_vols.csv")

sa <- rbind(May_sa,Dec_sa) %>%
  select(fragment_ID, Timepoint, surface.area.cm2) 
sa$ID <- paste0(sa$fragment_ID, sa$Timepoint)

# Load homogenate volumes data
homog.vol <- rbind(May_homog.vol, Dec_homog.vol) %>%
  select(fragment_ID, Timepoint, homog_vol_ml) 
homog.vol$ID <- paste0(homog.vol$fragment_ID, homog.vol$Timepoint)

# Load Coral sample metadata
info <- read_csv("data/metadata_POC_TPC.csv")
info$ID <- paste0(info$fragment_ID, info$Timepoint)

# Join homogenate volumes with sample metadata
metadata <- dplyr::inner_join(
   info,
   dplyr::select(homog.vol, -any_of(names(info)), ID),
   by = "ID"
)

#combine surface area with sample metadata
metadata <- dplyr::inner_join(
   metadata,
   dplyr::select(sa, -any_of(names(metadata)), ID),
   by = "ID"
)

# Join prot data with sample metadata
prot_host <- dplyr::inner_join(
   tpc.host.protein,
   dplyr::select(metadata, -any_of(names(tpc.host.protein)), ID),
   by = "ID"
)


# Standardize protein to volumne and surface area and mg/cm2
prot_host <- prot_host %>%
  mutate(prot_ug = prot_ug.mL * homog_vol_ml,
         prot_ug.cm2 = prot_ug / surface.area.cm2,
         prot_mg.cm2 = prot_ug.cm2 / 1000)


boxplot(prot_mg.cm2~Timepoint, data=prot_host)
```

#filter to Hap1a and Hap3b only and the same colonies for both times
```{r}
#filter by species
prot_host.sub<-prot_host %>% 
  filter(mtORF =="Haplotype_1a" | mtORF =="P verrucosa Haplotype 3b") 

#filter by colonies available in May and Dec
prot_host.sub.unique <- prot_host.sub %>% 
  group_by(fragment_ID) %>% 
  filter(n_distinct(Timepoint) == 2)

#calculate the mean of the 2 replicate  wells
prot_host.sub.unique.means <- prot_host.sub.unique %>% 
  group_by(fragment_ID, Timepoint, mtORF) %>% 
  summarise(prot_mg.cm2 = mean(prot_mg.cm2, na.rm = T))

```

#Statistical testing Host
```{r}

## Outlier Detection

# 2 way ANOVA
## Untransformed
model  <- lm(prot_mg.cm2 ~ mtORF*Timepoint, data = prot_host.sub.unique.means)
check_model(model)
check_outliers(model)
check_normality(model)

## log10 Transformed
model.1  <- lm(log10(prot_mg.cm2) ~ mtORF*Timepoint, data = prot_host.sub.unique.means)
check_model(model.1)
check_outliers(model.1)
check_normality(model.1)

model.Prot.Host  <- lm(prot_mg.cm2 ~ mtORF*Timepoint, data = prot_host.sub.unique.means)
anova(model.Prot.Host)
stat.labels1 <- round(anova(model.Prot.Host), 5)

```

```{r}
#summarize  mean and sem by site, species, and partner and plot

level_order <- c('May', 'Dec') 
prot_host.sub.unique.means$group <- paste0(prot_host.sub.unique.means$Timepoint, " ", prot_host.sub.unique.means$mtORF)

# Plot all data points with mean ± se
prot_plot_Host <- prot_host.sub.unique.means %>%
  ggplot(aes(x = factor(Timepoint, level = level_order), y = prot_mg.cm2, color = group, shape=mtORF, group = mtORF)) +
  labs(x = "", y = expression("Host Soluble Protein mg"~cm^{-2})) +
  geom_jitter(width = 0.3) +                                            # Plot all points
  stat_summary(fun.data = mean_cl_normal, fun.args = list(mult = 1),    # Plot standard error
               geom = "errorbar", width = 0.2) +
  stat_summary(fun = mean, geom = "point", size=3) +           # Plot mean
  stat_summary(aes(x = Timepoint, group = mtORF), fun = mean, geom = "line", alpha=0.2) +
  scale_color_manual(name="group", values=c( "orangered","cyan","orange", "aquamarine"))+
  geom_text(x=1, y=1.30, label=paste("Species=",stat.labels1$`Pr(>F)`[1]), size=3, color=ifelse(stat.labels1$`Pr(>F)`[1] < 0.05, "black", "darkgray")) + 
  geom_text(x=1, y=1.25, label=paste("Time=",stat.labels1$`Pr(>F)`[2]), size=3, color=ifelse(stat.labels1$`Pr(>F)`[2] < 0.05, "black", "darkgray")) + 
  geom_text(x=1, y=1.20, label=paste("Species x Time=",stat.labels1$`Pr(>F)`[3]), size=3, color=ifelse(stat.labels1$`Pr(>F)`[3] < 0.05, "black", "darkgray")) +
  theme(axis.text.y = element_text(size=14, face="bold", colour = "black"),axis.text.x = element_text(size=14, face="bold", colour = "black")) +
  theme_classic(base_size = 14)+
  theme(legend.position='none')
prot_plot_Host 

```


# 20220808 Holo
# Import data 
```{r}
# Load data
prot_data <- read.csv("data/protein/20220810_May_BCA_holobiont_data_prot.csv")         # List all files in directory
platemap <- read.csv("data/protein/20220810_May_BCA_holobiont_platemap_prot.csv")       # List platemap files
df_holo <- right_join(platemap, prot_data, by="Well") # Merge platemap and data for each plate

# Plot standard curve
# Create standard curve following kit instructions
standards_holo <- tribble(
  ~std, ~BSA_ug.mL,
  "A",        2000,
  "B",        1500,
  "C",        1000,
  "D",         750,
  "E",         500,
  "F",         250,
  "G",         125,
  "H",          25,
  "I",           0
)

std_curve_holo <- df_holo %>%
  filter(grepl("Standard", fragment_ID)) %>% #filter standards
  select(Well, fragment_ID, abs562 = "abs562") %>% #select columns
  rename(std = fragment_ID) %>% #name id
  mutate(std = str_sub(std, 9, 9)) %>% #remove the word standard
  mutate(abs562.adj = abs562 - abs562[std == "I"]) %>%       # subtract blank absorbance value from all
  left_join(standards_holo) #join with standard concentrations above

#Calculate the calibration curve
mod_holo <- lm(BSA_ug.mL ~ abs562, data = std_curve_holo) #fit linear model
fitted_holo <- mod_holo %>% broom::augment() #extract the model fitted data
summary(mod_holo) #report the model fit

# Plot standard curve with line fit
std_curve_plot_holo <- std_curve_holo %>%
  ggplot(aes(x = abs562, y = BSA_ug.mL)) + #plot x y
  geom_point(color = "red", size = 3)+ # color standards
  geom_line(data = fitted_holo, aes(x = abs562, y = .fitted)) + #add line fit
  stat_poly_eq(use_label(c("eq", "R2")),rr.digits = 4) + #show line fit equation and R2
  labs(title = "BSA Protein Standard curve") #label plot
std_curve_plot_holo #view plot

# Calculate protein concentration for all samples using standard curve
prot_holo <- df_holo %>%
  filter(!grepl("Standard", fragment_ID, Timepoint)) %>%  # Get just samples (not standards)
  select(Well, fragment_ID, Timepoint, abs562) %>%        # Select only needed columns
  filter(!is.na(fragment_ID)) %>%                         # Filter out empty wells
  filter(fragment_ID != "BK") %>%                         # Filter out blank wells
  mutate(prot_ug.mL = map_dbl(abs562, ~ predict(mod_holo, newdata = data.frame(abs562 = .))))    # Use standard curve to convert absorbance to protein

prot_holo <- na.omit(prot_holo) #remove rows with NA
prot_holo <- prot_holo %>% filter(prot_ug.mL > 0) #remove any rows with impossible values

#plot samples projected onto standards to check that they fall in range of the standards
std_curve_plot_holo + 
  geom_point(data = prot_holo, aes(x = abs562, y = prot_ug.mL), pch = "X", cex = 5, alpha = 0.3) + #add points
  labs(title = "All samples projected on standard curve") #label plot

#start dataframe to add all values to after plate specific calculations
tpc.holo.protein <- prot_holo

```

# 20220614 Holo
# Import data 
```{r}
# Load data
prot_data <- read.csv("data/protein/20230614_Dec_BCA_holobiont_data_prot.csv")         # List all files in directory
platemap <- read.csv("data/protein/20230614_Dec_BCA_holobiont_platemap_prot.csv")       # List platemap files
df_holo <- right_join(platemap, prot_data, by="Well") # Merge platemap and data for each plate

# Plot standard curve
# Create standard curve following kit instructions
standards_holo <- tribble(
  ~std, ~BSA_ug.mL,
  "A",        2000,
  "B",        1500,
  "C",        1000,
  "D",         750,
  "E",         500,
  "F",         250,
  "G",         125,
  "H",          25,
  "I",           0
)

std_curve_holo <- df_holo %>%
  filter(grepl("Standard", fragment_ID)) %>% #filter standards
  select(Well, fragment_ID, abs562 = "abs562") %>% #select columns
  rename(std = fragment_ID) %>% #name id
  mutate(std = str_sub(std, 9, 9)) %>% #remove the word standard
  mutate(abs562.adj = abs562 - abs562[std == "I"]) %>%       # subtract blank absorbance value from all
  left_join(standards_holo) #join with standard concentrations above

#Calculate the calibration curve
mod_holo <- lm(BSA_ug.mL ~ abs562, data = std_curve_holo) #fit linear model
fitted_holo <- mod_holo %>% broom::augment() #extract the model fitted data
summary(mod_holo) #report the model fit

# Plot standard curve with line fit
std_curve_plot_holo <- std_curve_holo %>%
  ggplot(aes(x = abs562, y = BSA_ug.mL)) + #plot x y
  geom_point(color = "red", size = 3)+ # color standards
  geom_line(data = fitted_holo, aes(x = abs562, y = .fitted)) + #add line fit
  stat_poly_eq(use_label(c("eq", "R2")),rr.digits = 4) + #show line fit equation and R2
  labs(title = "BSA Protein Standard curve") #label plot
std_curve_plot_holo #view plot

# Calculate protein concentration for all samples using standard curve
prot_holo <- df_holo %>%
  filter(!grepl("Standard", fragment_ID, Timepoint)) %>%  # Get just samples (not standards)
  select(Well, fragment_ID, Timepoint, abs562) %>%        # Select only needed columns
  filter(!is.na(fragment_ID)) %>%                         # Filter out empty wells
  filter(fragment_ID != "BK") %>%                         # Filter out blank wells
  mutate(prot_ug.mL = map_dbl(abs562, ~ predict(mod_holo, newdata = data.frame(abs562 = .))))    # Use standard curve to convert absorbance to protein

prot_holo <- na.omit(prot_holo) #remove rows with NA
prot_holo <- prot_holo %>% filter(prot_ug.mL > 0) #remove any rows with impossible values

#plot samples projected onto standards to check that they fall in range of the standards
std_curve_plot_holo + 
  geom_point(data = prot_holo, aes(x = abs562, y = prot_ug.mL), pch = "X", cex = 5, alpha = 0.3) + #add points
  labs(title = "All samples projected on standard curve") #label plot

#start dataframe to add all values to after plate specific calculations
tpc.holo.protein <- rbind(tpc.holo.protein, prot_holo)

```


# Normalize Holo protein to surface area
```{r}

tpc.holo.protein$ID <- paste0(tpc.holo.protein$fragment_ID, tpc.holo.protein$Timepoint)

# Join prot data with sample metadata
prot_holo <- dplyr::inner_join(
   tpc.holo.protein,
   dplyr::select(metadata, -any_of(names(tpc.holo.protein)), ID),
   by = "ID"
)


# Standardize protein to volumne and surface area and mg/cm2
prot_holo <- prot_holo %>%
  mutate(prot_ug = prot_ug.mL * homog_vol_ml,
         prot_ug.cm2 = prot_ug / surface.area.cm2,
         prot_mg.cm2 = prot_ug.cm2 / 1000)


boxplot(prot_mg.cm2~Timepoint, data=prot_holo)
```

#filter to Hap1a and Hap3b only and the same colonies for both times
```{r}
#filter by species
prot_holo.sub<-prot_holo %>% 
  filter(mtORF =="Haplotype_1a" | mtORF =="P verrucosa Haplotype 3b") 

#filter by colonies available in May and Dec
prot_holo.sub.unique <- prot_holo.sub %>% 
  group_by(fragment_ID) %>% 
  filter(n_distinct(Timepoint) == 2)

#calculate the mean of the 2 replicate  wells
prot_holo.sub.unique.means <- prot_holo.sub.unique %>% 
  group_by(fragment_ID, Timepoint, mtORF) %>% 
  summarise(prot_mg.cm2 = mean(prot_mg.cm2, na.rm = T))

```

#Statistical testing Holobiont
```{r}

## Outlier Detection

# 2 way ANOVA
## Untransformed
model  <- lm(prot_mg.cm2 ~ mtORF*Timepoint, data = prot_holo.sub.unique.means)
check_model(model)
check_outliers(model)
check_normality(model)

## log10 Transformed
model.1  <- lm(log10(prot_mg.cm2) ~ mtORF*Timepoint, data = prot_holo.sub.unique.means)
check_model(model.1)
check_outliers(model.1)
check_normality(model.1)

model.Prot.holo  <- lm(log10(prot_mg.cm2) ~ mtORF*Timepoint, data = prot_holo.sub.unique.means)
anova(model.Prot.holo)
stat.labels1 <- round(anova(model.Prot.holo), 5)

```



```{r}
#summarize  mean and sem by site, species, and partner and plot
# Plot all data points with mean ± se

prot_holo.sub.unique.means$group <- paste0(prot_holo.sub.unique.means$Timepoint, " ", prot_holo.sub.unique.means$mtORF)

prot_plot_Holo <- prot_holo.sub.unique.means %>%
  ggplot(aes(x = factor(Timepoint, level = level_order), y = prot_mg.cm2, color = group, shape=mtORF, group = mtORF)) +
  labs(x = "", y = expression("Holobiont Soluble Protein mg"~cm^{-2})) +
  geom_jitter(width = 0.3) +                                            # Plot all points
  stat_summary(fun.data = mean_cl_normal, fun.args = list(mult = 1),    # Plot standard error
               geom = "errorbar", width = 0.2) +
  stat_summary(fun = mean, geom = "point", size=3) +           # Plot mean
  stat_summary(aes(x = Timepoint, group = mtORF), fun = mean, geom = "line", alpha=0.2) +
  scale_color_manual(name="group", values=c( "orangered","cyan","orange", "aquamarine"))+
  geom_text(x=1, y=2.65, label=paste("Species=",stat.labels1$`Pr(>F)`[1]), size=3, color=ifelse(stat.labels1$`Pr(>F)`[1] < 0.05, "black", "darkgray")) + 
  geom_text(x=1, y=2.54, label=paste("Time=",stat.labels1$`Pr(>F)`[2]), size=3, color=ifelse(stat.labels1$`Pr(>F)`[2] < 0.05, "black", "darkgray")) + 
  geom_text(x=1, y=2.44, label=paste("Species x Time=",stat.labels1$`Pr(>F)`[3]), size=3, color=ifelse(stat.labels1$`Pr(>F)`[3] < 0.05, "black", "darkgray")) +
  theme(axis.text.y = element_text(size=14, face="bold", colour = "black"),axis.text.x = element_text(size=14, face="bold", colour = "black")) +
  theme_classic(base_size = 14)+
  theme(legend.position='none')
prot_plot_Holo 

```


<!-- ```{r} -->
<!--  (prot_plot_Holo+prot_plot_Host)  -->
<!--   ggsave("output/Poc_TPC_Protein_1a3b.pdf", plot = last_plot(), width = 12, height = 4) -->
<!--   ggsave("output/Poc_TPC_Protein_1a3b.jpg", plot = last_plot(), width = 12, height = 4) -->
<!-- ``` -->


```{r}

prot_holo.sub.unique.means$ID <- paste0(prot_holo.sub.unique.means$fragment_ID, prot_holo.sub.unique.means$Timepoint)
prot_host.sub.unique.means$ID <- paste0(prot_host.sub.unique.means$fragment_ID, prot_host.sub.unique.means$Timepoint)

data <- full_join(prot_holo.sub.unique.means,prot_host.sub.unique.means, by="ID")

data$Sym_prot_mg.cm2 <-data$prot_mg.cm2.x - data $prot_mg.cm2.y
```

#Statistical testing Holobiont
```{r}

## Outlier Detection

# 2 way ANOVA
## Untransformed
model  <- lm(Sym_prot_mg.cm2 ~ mtORF.x*Timepoint.x, data = data)
check_model(model)
check_outliers(model)
check_normality(model)

## log10 Transformed
model.1  <- lm(log10(Sym_prot_mg.cm2) ~ mtORF.x*Timepoint.x, data = data)
check_model(model.1)
check_outliers(model.1)
check_normality(model.1)

model.Prot.sym  <- lm(log10(Sym_prot_mg.cm2) ~ mtORF.x*Timepoint.x, data = data)
anova(model.Prot.sym)
stat.labels1 <- round(anova(model.Prot.sym), 5)

```



```{r}
#summarize  mean and sem by site, species, and partner and plot
# Plot all data points with mean ± se
data$group <- paste0(data$Timepoint.x, " ", data$mtORF.x)

prot_plot_Sym <- data %>%
  ggplot(aes(x = factor(Timepoint.x, level = level_order), y = Sym_prot_mg.cm2, color = group, shape=mtORF.x, group = mtORF.x)) +
  labs(x = "", y = expression("Symbiont Soluble Protein mg"~cm^{-2})) +
  geom_jitter(width = 0.3) +                                            # Plot all points
  stat_summary(fun.data = mean_cl_normal, fun.args = list(mult = 1),    # Plot standard error
               geom = "errorbar", width = 0.2) +
  stat_summary(fun = mean, geom = "point", size=3) +           # Plot mean
  stat_summary(aes(x = Timepoint.x, group = mtORF.x), fun = mean, geom = "line", alpha=0.2) +
  scale_color_manual(name="group", values=c( "orangered","cyan","orange", "aquamarine"))+
  geom_text(x=1, y=1.50, label=paste("Species=",stat.labels1$`Pr(>F)`[1]), size=3, color=ifelse(stat.labels1$`Pr(>F)`[1] < 0.05, "black", "darkgray")) + 
  geom_text(x=1, y=1.44, label=paste("Time=",stat.labels1$`Pr(>F)`[2]), size=3, color=ifelse(stat.labels1$`Pr(>F)`[2] < 0.05, "black", "darkgray")) + 
  geom_text(x=1, y=1.38, label=paste("Species x Time=",stat.labels1$`Pr(>F)`[3]), size=3, color=ifelse(stat.labels1$`Pr(>F)`[3] < 0.05, "black", "darkgray")) +
  theme(axis.text.y = element_text(size=14, face="bold", colour = "black"),axis.text.x = element_text(size=14, face="bold", colour = "black")) +
  theme_classic(base_size = 14)+
  theme(legend.position='none')
prot_plot_Sym 

```



```{r}
 (prot_plot_Host+prot_plot_Sym) 
  ggsave("output/Poc_TPC_Protein_Allpartner_1a3b.pdf", plot = last_plot(), width = 10, height = 4)
  ggsave("output/Poc_TPC_Protein_Allpartner_1a3b.jpg", plot = last_plot(), width = 10, height = 4)
```


