---
title: "Phys_Variables"
author: "HM Putnam"
date: "10/8/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

## install packages if you dont already have them
if (!require("tidyverse")) install.packages("tidyverse")
if (!require("plotrix")) install.packages("plotrix")
if (!require("broom")) install.packages("broom")
if (!require("gridExtra")) install.packages("gridExtra")

# load packages
library(tidyverse)
library(plotrix)
library(broom)
library(gridExtra)
```

# Biomass
```{r }
#Read in biomass data
Data <- read.csv("data/biomass_data.csv")
Data <- na.omit(Data)

# calculated mass per ml
#different volumes for sym (4ml) and host (5ml)
sym <- 4
host <- 5

#Load tissue homogenate volume
homog_vol <- read.csv("data/homogenate_vols.csv", header=TRUE)

# Load Surface area data
sa <- read.csv("data/TPC_surface.area.calc.csv")

# Coral sample metadata
metadata <- read_csv("data/metadata_POC_TPC.csv")

# Join homogenate volumes and surface area with sample metadata
metadata <- full_join(metadata, homog_vol) %>%
  full_join(sa)

#Standardize for volume input
Data <- Data %>%
  mutate(dry.pan.mass.g.ml = case_when(partner=="Sym" ~ dry.pan.mass.g/sym, partner=="Host" ~dry.pan.mass.g/host),
         burnt.pan.mass.g.ml = case_when(partner=="Sym" ~ burnt.pan.mass.g/sym, partner=="Host" ~burnt.pan.mass.g/host))

# Standardize for the total homogenate volume
Data <- left_join(Data, homog_vol)  %>%
  mutate(dry.pan.mass.g.vol.corr = dry.pan.mass.g.ml*homog_vol_ml, 
         burnt.pan.mass.g.vol.corr = burnt.pan.mass.g.ml*homog_vol_ml)

# Calculate Dry Biomass
dw <- left_join(Data, metadata) %>%
  mutate(dry.bioimass.g = (dry.pan.mass.g.vol.corr - initial.mass.g),
         DW.mg.cm2 = ((dry.bioimass.g)*1000) / surface.area.cm2)

# Calculate AFDW
afdw <- left_join(Data, metadata) %>%
  mutate(dry.bioimass.g = (dry.pan.mass.g.vol.corr - burnt.pan.mass.g.vol.corr),
         AFDW.mg.cm2 = ((dry.bioimass.g)*1000) / surface.area.cm2)


```

# Summarize AFDW and Dry Biomass data and Output to .csv.  
```{r}
afdw<-afdw %>%
  group_by(fragment_ID, partner)%>%
  summarise(AFDW.mg.cm2=mean(AFDW.mg.cm2))%>%
  left_join(.,metadata)%>% #add metadata back into file
  select(fragment_ID, partner, Morphology, AFDW.mg.cm2)

dw<-dw %>% 
  group_by(fragment_ID, partner)%>%
  summarise(DW.mg.cm2=mean(DW.mg.cm2))%>%
  left_join(.,metadata)%>% #add metadata back into file
  select(fragment_ID, partner, Morphology, DW.mg.cm2) 
  
output<-left_join(afdw,dw)%>%
  write_csv(path = "output/biomass.csv")
```

# Plot Dry Biomass
```{r}
# Plot all data points with mean ± se
Dry.Biomass <- dw %>%
  ggplot(aes(x = Morphology, y = DW.mg.cm2, color = Morphology)) +
  scale_color_manual(name="Morphology", values=c("orange","black", "cyan"))+
  #coord_cartesian(ylim = c(0, 1.8))+
  labs(x = "", y = expression("Dry Biomass mg"~cm^{-2})) +
  geom_jitter(width = 0.1) +                                            # Plot all points
  stat_summary(fun.data = mean_cl_normal, fun.args = list(mult = 1),    # Plot standard error
               geom = "errorbar", color = "black", width = 0.5) +
  stat_summary(fun = mean, geom = "point", color = "black") +           # Plot mean
  theme_bw(base_size = 12)+ theme(legend.position="none")+
  facet_wrap("partner",
             labeller = labeller(partner = 
    c("Host" = "Coral",
      "Sym" = "Symbiont"))) 
Dry.Biomass 
```
# Plot AFDW
```{r}

# Plot all data points with mean ± se
AFDW <- afdw %>%
  ggplot(aes(x = Morphology, y = AFDW.mg.cm2, color = Morphology)) +
  scale_color_manual(name="Morphology", values=c("orange","black", "cyan"))+
  #coord_cartesian(ylim = c(0, 5))+
  labs(x = "", y = expression("AFDW mg"~cm^{-2})) +
  geom_jitter(width = 0.1) +                                            # Plot all points
  stat_summary(fun.data = mean_cl_normal, fun.args = list(mult = 1),    # Plot standard error
               geom = "errorbar", color = "black", width = 0.5) +
  stat_summary(fun = mean, geom = "point", color = "black") +           # Plot mean
  theme_bw(base_size = 12)+ theme(legend.position="none")+
  facet_wrap("partner",
             labeller = labeller(partner = 
    c("Host" = "Coral",
      "Sym" = "Symbiont"))) 
AFDW
```

#Chlorophyll
```{r}
# Define function to read in chl data
read_chl <- function(file) {
  chl_data <- read_csv(file, skip = 24, n_max = 24) %>%
    select(-1) %>%
    magrittr::set_colnames(c("row", 1:12, "wavelength")) %>%
    fill(row) %>%
    gather("col", "absorbance", -wavelength, -row) %>%
    unite("well", c(row, col), sep = "")
}

# List chlorophyll data files
chl_path <- "data/"                                        # Path to chlorophyll data directory
all_chl_files <- list.files(path = chl_path, pattern = "_Chl_data.csv")          # List all files in directory
chl_platemaps <- list.files(path = chl_path, pattern = "Chl_platemap")       # List platemap files
chl_data_files <- setdiff(all_chl_files, chl_platemaps)                  # List absorbance data files


# Read in all files into tibble
df <- tibble(file = chl_data_files) %>%
  mutate(platemap = map(file, ~ read_csv(paste0(chl_path, tools::file_path_sans_ext(.), "_platemap.csv"))),
         chl_data = map(file, ~ read_chl(paste0(chl_path, .))))

# Merge platemap and data for each plate
df <- df %>%
  mutate(merged = map2(platemap, chl_data, ~ right_join(.x, .y)))
```

# Calculate chlorophyll concentrations
```{r}
# average all technical replicates for each plate/sample/wavelength, including all acetone blanks together (per plate)
df <- df %>%
  unnest(merged) %>%
  filter(!is.na(fragment_ID)) %>%                         # remove empty wells (fragment_ID is NA)
  group_by(file, fragment_ID, wavelength) %>%
  summarise(n = n(), mean_abs = mean(absorbance)) %>%
  spread(wavelength, mean_abs)

# get the acetone blank 750 absorbace for each file (i.e., plate), and subtract from 630 and 663 values for each sample
df <- df %>%
  group_by(file) %>%
  mutate(blank750 = `750`[fragment_ID == "BK"]) %>%
  ungroup() %>%
  mutate(adj630 = `630` - blank750,
         adj663 = `663` - blank750)

# calculate chla and chlc2 values based on equations from Jeffrey and Humphrey 1975
# chla = (11.43 * adj663) - (0.64 * adj630)
# chlc2 =  (27.09 * adj630) - (3.63 * adj663)
# units µg/ml
#path length adjustment = 0.6 

df <- df %>%
  mutate(chla.ug.ml = (11.43 * adj663)/0.6 - (0.64 * adj630)/0.6,
        chlc2.ug.ml = (27.09 * adj630)/0.6 - (3.63 * adj663)/0.6)

```

# Normalize chl to surface area
```{r}
# Load homogenate volume
homog.vol <- read_csv("data/homogenate_vols.csv") %>%
  select(fragment_ID, homog_vol_ml)

chl <- full_join(df, homog.vol)

# Load Surface area data
sa <- read.csv("data/TPC_surface.area.calc.csv")

# Coral sample metadata
metadata <- read_csv("data/metadata_POC_TPC.csv")

# Join homogenate volumes and surface area with sample metadata
chl <- full_join(metadata, chl) %>%
  full_join(sa) %>%
  full_join(chl)

# Multiply chlorophyll by the homogenate volume and divide by surface area
chl <- chl %>%
  mutate(chla.ug.cm2 = chla.ug.ml * homog_vol_ml / surface.area.cm2,
         chlc2.ug.cm2 = chlc2.ug.ml * homog_vol_ml / surface.area.cm2)

# remove blanks and NAs
chl <- filter(chl, !fragment_ID %in% c("NA", "BK"))

# write chlorophyll data to file
chl %>%
  select(fragment_ID, Morphology,chla.ug.cm2, chlc2.ug.cm2) %>%
  filter(!is.na(chla.ug.cm2))%>%
  filter(!is.na(chlc2.ug.cm2))%>%
  write_csv(path = "output/TPC_chlorophyll.csv")
```

# Plot results by species and site
```{r, eval = TRUE}

chl.all <- chl %>% pivot_longer(cols= chla.ug.cm2:chlc2.ug.cm2 ,
                                values_to="chl.ug.cm2") 

Chl <- chl.all %>%
  ggplot(aes(x = Morphology, y = chl.ug.cm2, color = Morphology)) +
  scale_color_manual(name="Morphology", values=c("orange","black", "cyan"))+
  #coord_cartesian(ylim = c(0, 5))+
  labs(x = "", y = expression("Chl mg"~cm^{-2})) +
  geom_jitter(width = 0.1) +                                            # Plot all points
  stat_summary(fun.data = mean_cl_normal, fun.args = list(mult = 1),    # Plot standard error
               geom = "errorbar", color = "black", width = 0.5) +
  stat_summary(fun = mean, geom = "point", color = "black") +           # Plot mean
  theme_bw(base_size = 12)+ theme(legend.position="none")+
  facet_wrap("name",
             labeller = labeller(name = 
    c("chla.ug.cm2" = "Chl-a",
      "chlc2.ug.cm2" = "Chl-c2"))) 
Chl
```

#Sym Density
# Import data
```{r} 
# Cell count data
sym_counts <- read_csv("data/TPC_POC_symbiont_counts.csv")

# Load Surface area data
sa <- read.csv("data/TPC_surface.area.calc.csv")

homog.vol <- read_csv("data/homogenate_vols.csv") %>%
  select(fragment_ID, homog_vol_ml)

# Coral sample metadata
metadata <- read_csv("data/metadata_POC_TPC.csv")

# Join homogenate volumes and surface area with sample metadata
metadata <- full_join(metadata, homog.vol)  %>%
  full_join(sa)

```

# Calculate cells per square centimeter
```{r}
# Calculate mean counts for each sample
sym_counts <- sym_counts %>%
  select(fragment_ID, Squares.Counted, matches("Count[0-9]")) %>%
  gather("rep", "count", -fragment_ID, -Squares.Counted) %>%
  group_by(fragment_ID, Squares.Counted) %>%
  summarise(mean_count = mean(count, na.rm = TRUE))

# Join mean counts with sample metadata
sym_counts <- full_join(sym_counts, metadata)

# Normalize counts by homogenat volume and surface area
sym_counts <- sym_counts %>%
  mutate(cells.mL = mean_count * 10000 / Squares.Counted,
         cells = cells.mL * homog_vol_ml,
         cells.cm2 = cells / surface.area.cm2)
```



# Plot data
```{r}
# Plot all data points with mean ± se
sym_counts$partner <- "Holobiont"
Sym <- sym_counts %>%
  ggplot(aes(x = Morphology, y = cells.cm2 / 10^6, color = Morphology)) +
  scale_color_manual(name="Morphology", values=c("orange","black", "cyan"))+
  #coord_cartesian(ylim = c(0, 1.8))+
  labs(x = "", y = expression("Cell Density (" *x*"10"^"6" *~cells *~ cm^"-2"*")")) +
  geom_jitter(width = 0.1) +                                            # Plot all points
  stat_summary(fun.data = mean_cl_normal, fun.args = list(mult = 1),    # Plot standard error
               geom = "errorbar", color = "black", width = 0.5) +
  stat_summary(fun = mean, geom = "point", color = "black") +           # Plot mean
  theme_bw(base_size = 12)+
  facet_wrap("partner",
             labeller = labeller(name = 
    c("Holobiont" = "Holobiont"))) 
Sym
```


Output data to file.  

```{r}
sym_counts %>%
  select(fragment_ID, Morphology, cells.cm2) %>%
  write_csv(path = "output/sym_counts.csv")


```

#Protein
# Import data for host protein 
```{r}
# List protein data files 
prot_path = "data/"  # Path to prot data directory
all_prot_files <- list.files(path = prot_path, pattern = "*_host")          # List all files in directory
prot_platemaps <- list.files(path = prot_path, pattern = "_host_platemap_prot")       # List platemap files
prot_data_files <- setdiff(all_prot_files, prot_platemaps)                 # List data files

# Read in all files into tibble
df_host <- tibble(file = prot_data_files) %>%
  separate(file, into = c("trip", "date", "plate"), remove = FALSE) %>%
  unite(plate, trip, date, plate) %>%
  dplyr::mutate(platemap = map(plate, ~read_csv(paste0(prot_path, ., "_platemap_prot.csv"))),
         prot_data = map(file, ~read_csv(paste0(prot_path, .)) %>% rename(well = Well)))

# Merge platemap and data for each plate
df_host <- df_host %>%
  mutate(merged = map2(platemap, prot_data, ~ right_join(.x, .y)))
```

# Plot standard curve
```{r}
# Create standard curve following kit instructions
standards_host <- tribble(
  ~std, ~BSA_ug.mL,
  "A",        2000,
  "B",        1500,
  "C",        1000,
  "D",         750,
  "E",         500,
  "F",         250,
  "G",         125,
  "H",          25,
  "I",           0
)

std_curve_host <- df_host %>%
  unnest(merged) %>%
  filter(grepl("Standard", fragment_ID)) %>%
  select(plate, well, fragment_ID, abs562 = `562:562`) %>%
  rename(std = fragment_ID) %>%
  mutate(std = str_sub(std, 9, 9)) %>%
  #group_by(std) %>%
  #summarise(abs562 = mean(abs562)) %>%                       # calculate mean of standard duplicates
  #mutate(abs562.adj = abs562 - abs562[std == "I"]) %>%       # subtract blank absorbace value from all
  left_join(standards_host)


## Fit nonlinear model for standard curve
mod_host <- nls(formula = BSA_ug.mL ~ z + a * exp(b * abs562), start = list(z = 0, a = 1, b = 1), data = std_curve_host)
fitted_host <- mod_host %>% broom::augment()

# Plot standard curve
std_curve_plot_host <- std_curve_host %>%
  ggplot(aes(x = abs562, y = BSA_ug.mL)) +
  geom_point(color = "red", size = 3) 

std_curve_plot_host + 
  geom_line(data = fitted_host, aes(x = abs562, y = .fitted)) +
  labs(title = "Standard curve")
```

# Calculate protein concentrations
```{r}
# Calculate protein concentration for all samples using standard curve
prot_host <- df_host %>%
  unnest(merged) %>%
  filter(!grepl("Standard", fragment_ID)) %>%                     # Get just samples (not standards)
  select(plate, well, fragment_ID, abs562 = `562:562`) %>%        # Select only needed columns
  filter(!is.na(fragment_ID)) %>%                                 # Filter out empty wells
  filter(fragment_ID != "BK") %>%                                 # Filter out blank wells
  mutate(prot_ug.mL = map_dbl(abs562, ~ predict(mod_host, newdata = data.frame(abs562 = .))))    # Use standard curve to convert absorbance to protein

std_curve_plot_host + 
  geom_point(data = prot_host, aes(x = abs562, y = prot_ug.mL), pch = "X", cex = 5, alpha = 0.3) +
  labs(title = "All samples projected on standard curve")
```

# Normalize to surface area
```{r}
# Surface area data
sa <- read.csv("data/TPC_surface.area.calc.csv")

# Tissue homogenate volume data
homog_vols <- read_csv("data/homogenate_vols.csv") %>% select(1:3)

# Coral sample metadata
metadata <- read_csv("data/metadata_POC_TPC.csv") %>% select(1:4)

# Join homogenate volumes and surface area with sample metadata
metadata <- full_join(metadata, homog_vols) %>%
  full_join(sa)

# Join prot data with metadata
prot_host <- left_join(prot_host, metadata) %>%
  mutate(prot_ug = prot_ug.mL * homog_vol_ml,
         prot_ug.cm2 = prot_ug / surface.area.cm2,
         prot_mg.cm2 = prot_ug.cm2 / 1000)
prot_host <- prot_host %>%
  filter(species=="Pocillopora") 

avg_prot_host <- prot_host %>%
  group_by(fragment_ID,Morphology) %>%
  summarize(prot_mg.cm2 = mean(prot_mg.cm2))

```

# Plot results by species and site
```{r}
# Plot all data points with mean ± se
avg_prot_host %>%
  ggplot(aes(x = Morphology, y = prot_mg.cm2, color = Morphology)) +
  scale_color_manual(name="Morphology", values=c("orange","black", "cyan"))+
  coord_cartesian(ylim = c(0, 1.8))+
  labs(x = "", y = expression("Host Soluble Protein mg"~cm^{-2})) +
  geom_jitter(width = 0.1) +                                            # Plot all points
  stat_summary(fun.data = mean_cl_normal, fun.args = list(mult = 1),    # Plot standard error
               geom = "errorbar", color = "black", width = 0.5) +
  stat_summary(fun = mean, geom = "point", color = "black")+           # Plot mean
  theme_bw(base_size = 12)
```

# Write data to output file
```{r}
# Write protein data to output file
prot_host %>%
  filter(!is.na(species)) %>%
  group_by(fragment_ID) %>%
  summarise(prot_ug = mean(prot_ug, na.rm = T),
            prot_ug.cm2 = mean(prot_ug.cm2, na.rm = T)) %>%
  select(fragment_ID, prot_ug, prot_ug.cm2) %>%
  write_csv(., path = "output/host_protein.csv")
```


# Import data for holobiont protein
```{r}
# List protein data files 
prot_path = "data/"                                              # Path to prot data directory
all_prot_files <- list.files(path = prot_path, pattern = "_holobiont")          # List all files in directory
prot_platemaps <- list.files(path = prot_path, pattern = "_holobiont_platemap_prot")       # List platemap files
prot_data_files <- setdiff(all_prot_files, prot_platemaps)                 # List data files

# Read in all files into tibble
df_holobiont <- tibble(file = prot_data_files) %>%
  separate(file, into = c("trip", "date", "plate"), remove = FALSE) %>%
  unite(plate, trip, date, plate) %>%
  dplyr::mutate(platemap = map(plate, ~read_csv(paste0(prot_path, ., "_platemap_prot.csv"))),
         prot_data = map(file, ~read_csv(paste0(prot_path, .)) %>% rename(well = Well)))

# Merge platemap and data for each plate
df_holobiont <- df_holobiont %>%
  mutate(merged = map2(platemap, prot_data, ~ right_join(.x, .y)))
```

# Plot standard curve
```{r}
# Create standard curve following kit instructions
standards_holobiont <- tribble(
  ~std, ~BSA_ug.mL,
  "A",        2000,
  "B",        1500,
  "C",        1000,
  "D",         750,
  "E",         500,
  "F",         250,
  "G",         125,
  "H",          25,
  "I",           0
)

std_curve_holobiont <- df_holobiont %>%
  unnest(merged) %>%
  filter(grepl("Standard", fragment_ID)) %>%
  select(plate, well, fragment_ID, abs562 = `562:562`) %>%
  rename(std = fragment_ID) %>%
  mutate(std = str_sub(std, 9, 9)) %>%
  #group_by(std) %>%
  #summarise(abs562 = mean(abs562)) %>%                       # calculate mean of standard duplicates
  #mutate(abs562.adj = abs562 - abs562[std == "I"]) %>%       # subtract blank absorbace value from all
  left_join(standards_holobiont)

## Fit nonlinear model for standard curve
mod_holobiont <- nls(formula = BSA_ug.mL ~ z + a * exp(b * abs562), start = list(z = 0, a = 1, b = 1), data = std_curve_holobiont)
fitted_holobiont <- mod_holobiont %>% broom::augment()

# Plot standard curve
std_curve_plot_holobiont <- std_curve_holobiont %>%
  ggplot(aes(x = abs562, y = BSA_ug.mL)) +
  geom_point(color = "red", size = 3) 

std_curve_plot_holobiont + 
  geom_line(data = fitted_holobiont, aes(x = abs562, y = .fitted)) +
  labs(title = "Standard curve")
```

# Calculate protein concentrations
```{r}
# Calculate protein concentration for all samples using standard curve
prot_holobiont <- df_holobiont %>%
  unnest(merged) %>%
  filter(!grepl("Standard", fragment_ID)) %>%                     # Get just samples (not standards)
  select(plate, well, fragment_ID, abs562 = `562:562`) %>%        # Select only needed columns
  filter(!is.na(fragment_ID)) %>%                                 # Filter out empty wells
  filter(fragment_ID != "BK") %>%                                 # Filter out blank wells
  mutate(prot_ug.mL = map_dbl(abs562, ~ predict(mod_holobiont, newdata = data.frame(abs562 = .))))    # Use standard curve to convert absorbance to protein

std_curve_plot_holobiont + 
  geom_point(data = prot_holobiont, aes(x = abs562, y = prot_ug.mL), pch = "X", cex = 5, alpha = 0.3) +
  labs(title = "All samples projected on standard curve")
```

# Normalize to surface area
```{r}

# Join prot data with metadata
prot_holobiont <- left_join(prot_holobiont, metadata) %>%
  mutate(prot_ug = prot_ug.mL * homog_vol_ml,
         prot_ug.cm2 = prot_ug / surface.area.cm2,
         prot_mg.cm2 = prot_ug.cm2 / 1000)

prot_holobiont <- prot_holobiont %>%
  filter(species=="Pocillopora") 

avg_prot_holobiont  <- prot_holobiont  %>%
  group_by(fragment_ID, Morphology) %>%
  summarize(prot_mg.cm2 = mean(prot_mg.cm2))
```

# Plot results by species and site
```{r}
# Plot all data points with mean ± se
prot_holobiont %>%
  ggplot(aes(x = Morphology, y = prot_mg.cm2, color = Morphology)) +
  scale_color_manual(name="Morphology", values=c("orange","black", "cyan"))+
  coord_cartesian(ylim = c(0, 1.8))+
  labs(x = "", y = expression("Holobiont Soluble Protein mg"~cm^{-2})) +
  geom_jitter(width = 0.1) +                                            # Plot all points
  stat_summary(fun.data = mean_cl_normal, fun.args = list(mult = 1),    # Plot standard error
               geom = "errorbar", color = "black", width = 0.5) +
  stat_summary(fun = mean, geom = "point", color = "black") +           # Plot mean
  theme_bw(base_size = 12) +theme(legend.position="none")
```

# Write data to output file
```{r}
# Write protein data to output file
prot_holobiont %>%
  filter(!is.na(species)) %>%
  group_by(fragment_ID) %>%
  summarise(prot_ug = mean(prot_ug, na.rm = T),
            prot_ug.cm2 = mean(prot_ug.cm2, na.rm = T)) %>%
  select(fragment_ID, prot_ug, prot_ug.cm2) %>%
  mutate(timepoint="MARCH")%>%
  write_csv(., path = "output/holobiont_protein.csv")
```

#Plot together
```{r}
avg_prot_holobiont$partner <- "Holobiont"
avg_prot_host$partner <- "Host"
prot.all <- rbind(avg_prot_holobiont, avg_prot_host)

Prot <- prot.all %>%
  ggplot(aes(x = Morphology, y = prot_mg.cm2, color = Morphology)) +
  scale_color_manual(name="Morphology", values=c("orange","black", "cyan"))+
  #coord_cartesian(ylim = c(0, 5))+
  labs(x = "", y = expression("Soluble Protein mg"~cm^{-2})) +
  geom_jitter(width = 0.1) +                                            # Plot all points
  stat_summary(fun.data = mean_cl_normal, fun.args = list(mult = 1),    # Plot standard error
               geom = "errorbar", color = "black", width = 0.5) +
  stat_summary(fun = mean, geom = "point", color = "black") +           # Plot mean
  theme_bw(base_size = 12)+ theme(legend.position="none")+
  facet_wrap("partner",
             labeller = labeller(name = 
    c("Holobiont" = "Holobiont",
      "Host" = "Host"))) 
Prot
```
#Plot all Phys
```{r}
grid.arrange(Dry.Biomass,AFDW,Prot,
         Chl, Sym, nrow = 2)

 g <- arrangeGrob(Dry.Biomass,AFDW,Prot,
         Chl, Sym, nrow = 2) #generates g
 ggsave(file= "output/Phys.pdf", g, width=16, height=6) #saves g
```