---
title: Larval thermal performance curves  
author: "AS Huffmyer"
date: '2021'
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_depth: 6
    toc_float: yes
  pdf_document:
    keep_tex: yes
editor_options: 
  chunk_output_type: console
---
This script analyzes and plots Pocillpora acuta larval 2021 respirometry data for thermal performance curves.  

# **Setup**  
Set up workspace and set knit options 
```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
set.seed(2222)
```

# **Install and load required packages**
```{r, warning=FALSE, message=FALSE}
## install packages if you dont already have them in your library
if ("ggplot2" %in% rownames(installed.packages()) == 'FALSE') install.packages('ggplot2')
if ("tidyverse" %in% rownames(installed.packages()) == 'FALSE') install.packages('tidyverse') 
if ("car" %in% rownames(installed.packages()) == 'FALSE') install.packages('car') 
if ("scales" %in% rownames(installed.packages()) == 'FALSE') install.packages('scales') 
if ("nls.multstart" %in% rownames(installed.packages()) == 'FALSE') install.packages('nls.multstart') 
if ("broom" %in% rownames(installed.packages()) == 'FALSE') install.packages('broom') 
if ("rTPC" %in% rownames(installed.packages()) == 'FALSE') remotes::install_github("padpadpadpad/rTPC")
if ("ggstatsplot" %in% rownames(installed.packages()) == 'FALSE') remotes::install_github("IndrajeetPatil/ggstatsplot")
if ("ggpubr" %in% rownames(installed.packages()) == 'FALSE') install.packages('ggpubr') 

#load packages
library("ggplot2")
library("tidyverse")
library('car')
library('scales')
library('nls.multstart')
library('broom')
library('rTPC')
library('ggstatsplot')
library('ggpubr')
```


# **Data visualization**  
Load data from LoLinR.    
```{r, warning=FALSE, message=FALSE}
#With Categorical Temps
PRdata<-read.csv("Pacu2021/Output/Respiration/TPC/oxygen_Resp_rates.csv") #load data
```

Format data columns.  
```{r, warning=FALSE, message=FALSE}
#remove all rows of wells that did not have samples or blanks
PRdata<-PRdata[!is.na(PRdata$Type),]

#format columns
PRdata$Temperature<-as.factor(PRdata$Temperature)
PRdata$Temperature<-as.numeric(as.character(PRdata$Temperature))
PRdata$Treatment<-as.factor(PRdata$Treatment)
#PRdata$Plate<-as.factor(PRdata$Plate)
PRdata$Run<-as.factor(PRdata$Run)

# calculate absolute rates and set temp and rate column names
PRdata <- PRdata %>%
    group_by(Temperature,Treatment)%>%
    mutate(abs=abs(R.nmol.org.min))%>%
    summarise(rate=abs) %>%
    mutate(temp=Temperature)

# add a group name by pasting Temperature and Treatment
PRdata$group <- paste0(PRdata$Temperature,"_", PRdata$Treatment)

# Visualize data
r_plot<-PRdata %>%
    ggplot(., aes(x = Temperature, y = rate, colour=Treatment)) +
    geom_point(aes(fill=Treatment, group=interaction(Temperature, Treatment)), pch = 21, size=2, alpha=0.5) + 
    xlab("Temperature") + 
    scale_fill_manual(name="Treatment", values=c("#3450A3","#E9A33D"))+
    scale_color_manual(name="Treatment", values=c("#3450A3","#E9A33D"))+
    ylab(expression(bold(paste("R (nmol ", O[2], " larva"^-1, "min"^-1, ")")))) +
    theme_classic() + 
    theme(legend.position="none",
      axis.title=element_text(face="bold", size=16),
      axis.text=element_text(size=12, color="black"), 
      legend.title=element_text(face="bold", size=14), 
      legend.text=element_text(size=12)); r_plot

ggsave("Pacu2021/Figures/Respiration/TPC/Respiration_Scatter_withOutliers.pdf", r_plot, dpi=300, w=8, h=8, units="in")
```

View and remove outliers.   
```{r, warning=FALSE, message=FALSE}
#identify outliers by Temperature and Treatment groups
outlier.plot <- ggbetweenstats(PRdata,group, rate, outlier.tagging = TRUE)
outlier.plot
ggsave("Pacu2021/Figures/Respiration/TPC/outliersbygroup.pdf", outlier.plot, dpi=300, w=16, h=8, units="in")

#set quantile values
q <- c(0.25, 0.75)

# calculate quantile values by Temperature and Treatment groups
Quants <- PRdata %>%
  group_by(Treatment, Temperature) %>%
  summarize(quant25 = quantile(rate, probs = q[1]),
            quant75 = quantile(rate, probs = q[2]),
            IQRbyGroup=IQR(rate))

# add a group name by pasting Temperature and Treatment
Quants$group <-paste0(Quants$Temperature,"_", Quants$Treatment)

#Calculate Quantile upper and lower ranges 
Quants$upper <-  Quants$quant75+1.5*Quants$IQRbyGroup # Upper Range  
Quants$lower <- Quants$quant25-1.5*Quants$IQRbyGroup # Lower Range

#join outlier cutoffs with rate data
PRdata <- left_join(PRdata, Quants)

#remove outliers from rates
PRdata <- PRdata %>%
  filter(rate < upper) %>%
  filter(rate > lower) #%>%
  #filter(rate < 0.125)

# Visualize data following outlier removal
r_plot<-PRdata %>%
    ggplot(., aes(x = Temperature, y = rate, colour=Treatment)) +
    geom_point(aes(fill=Treatment, group=interaction(Temperature, Treatment)), pch = 21, size=2, alpha=0.5) + 
    xlab("Temperature") + 
    scale_fill_manual(name="Treatment", values=c("#3450A3","#E9A33D"))+
    scale_color_manual(name="Treatment", values=c("#3450A3","#E9A33D"))+
    ylab(expression(bold(paste("R (nmol ", O[2], " larva"^-1, "min"^-1, ")")))) +
    theme_classic() + 
    theme(legend.position="none",
      axis.title=element_text(face="bold", size=16),
      axis.text=element_text(size=12, color="black"), 
      legend.title=element_text(face="bold", size=14), 
      legend.text=element_text(size=12)); r_plot

ggsave("Pacu2021/Figures/Respiration/TPC/Respiration_Scatter_afterOutliersRemoved.pdf", r_plot, dpi=300, w=8, h=8, units="in")

```

Filtering curve to environmentally relevant Temperatures 22-34°C
```{r}

#Filtering out data from Temperatures below 21 and above 33
PRdata <- PRdata %>%
    filter(!Temperature<20) %>%
    filter(!Temperature>36.51)

# Visualize data following range filtering
r_plot<-PRdata %>%
    ggplot(., aes(x = Temperature, y = rate, colour=Treatment)) +
    geom_point(aes(fill=Treatment, group=interaction(Temperature, Treatment)), pch = 21, size=2, alpha=0.5) + 
    xlab("Temperature") + 
    scale_fill_manual(name="Treatment", values=c("#3450A3","#E9A33D"))+
    scale_color_manual(name="Treatment", values=c("#3450A3","#E9A33D"))+
    ylab(expression(bold(paste("R (nmol ", O[2], " larva"^-1, "min"^-1, ")")))) +
    theme_classic() + 
    theme(legend.position="none",
      axis.title=element_text(face="bold", size=16),
      axis.text=element_text(size=12, color="black"), 
      legend.title=element_text(face="bold", size=14), 
      legend.text=element_text(size=12)); r_plot

ggsave("Pacu2021/Figures/Respiration/TPC/Respiration_Scatter_Filtered.pdf", r_plot, dpi=300, w=8, h=8, units="in")

```

# **Statistical Analysis**    

TPC fitting 
Padifeld et al **rTPC and nls.multstart: A new pipeline to fit thermal performance curves in r**  
https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/2041-210X.13585  

Sharpe Schoolfield 1981 model
Schoolfield, R. M., Sharpe, P. J. H., & Magnuson, C. E. (1981). Non-linear regression of biological temperature-dependent rate models based on absolute reaction-rate theory. Journal of theoretical biology, 88(4), 719-731. https://doi.org/10.1016/0022-5193(81)90246-0

```{r}

# choose model
get_model_names()
#sharpeschoolhigh_1981

# get start vals
start_vals <- get_start_vals(PRdata$temp,PRdata$rate, model_name = 'sharpeschoolhigh_1981')

# get limits
low_lims <- get_lower_lims(PRdata$temp,PRdata$rate, model_name = 'sharpeschoolhigh_1981')
upper_lims <- get_upper_lims(PRdata$temp,PRdata$rate, model_name = 'sharpeschoolhigh_1981')

#view values
start_vals
low_lims
upper_lims

# AMBIENT CURVE FIT
d.amb <- PRdata %>% 
  filter(Treatment=="Ambient")

#fit 
amb.fit <- nls_multstart(rate~sharpeschoolhigh_1981(temp = temp, r_tref,e,eh,th, tref = 28),
                                                     data = d.amb,
                                                     iter = 500,
                                                     start_lower = start_vals - 1,
                                                     start_upper = start_vals + 1,
                                                     lower = low_lims,
                                                     upper = upper_lims,
                                                     supp_errors = 'Y')

amb.fit

#generate the predicted data
amb_new_data <- data.frame(temp = seq(min(d.amb$temp), max(d.amb$temp), 0.5))
amb.preds <- augment(amb.fit, newdata = amb_new_data)

#calculate TPC parameters
amb.TCP.res <- calc_params(amb.fit) %>%
  mutate_all(round, 2)   # round 

amb.TCP.res 

```


### Bootstrapping ambient curve fit    

Resampling the original data with replacement
```{r}
# refit model using nlsLM
amb.fit_nlsLM <- minpack.lm::nlsLM(rate~sharpeschoolhigh_1981(temp = temp, r_tref,e,eh,th, tref = 28),
                        data = d.amb,
                        start = coef(amb.fit),
                        lower = low_lims,
                        upper = upper_lims,
                        weights = rep(1, times = nrow(d.amb)))

# bootstrap using case resampling
amb.boot1 <- Boot(amb.fit_nlsLM, method = 'case')

# look at the data
head(amb.boot1$t)


# create predictions of each bootstrapped model
amb.boot1_preds <- amb.boot1$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = 1:n()) %>%
  group_by_all() %>%
  do(data.frame(temp = seq(min(d.amb$temp), max(d.amb$temp), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = sharpeschoolhigh_1981(temp, r_tref, e, eh, th, tref = 28))

# calculate bootstrapped confidence intervals
amb.boot1_conf_preds <- group_by(amb.boot1_preds, temp) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

# plot bootstrapped CIs
amb.CI.plot <- ggplot() +
  geom_line(aes(temp, .fitted), amb.preds, col = '#3450A3') +
  geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), amb.boot1_conf_preds, fill = '#3450A3', alpha = 0.3) +
  geom_point(aes(temp, rate), d.amb, size = 2, alpha = 0.5,col = '#3450A3') +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration Rate (nmol O2/larva/min')
amb.CI.plot 

```


```{r}
# HIGH CURVE FIT
d.high <- PRdata %>% 
  filter(Treatment=="High")

# choose model
mod <- 'sharpschoolhigh_1981'

#fit 
high.fit <- nls_multstart(rate~sharpeschoolhigh_1981(temp = temp, r_tref,e,eh,th, tref = 28),
                                                     data = d.high,
                                                     iter = 500,
                                                     start_lower = start_vals - 1,
                                                     start_upper = start_vals + 1,
                                                     lower = low_lims,
                                                     upper = upper_lims,
                                                     supp_errors = 'Y')

high.fit

#generate the predicted data
high_new_data <- data.frame(temp = seq(min(d.high$temp), max(d.high$temp), 0.5))
high.preds <- augment(high.fit, newdata = high_new_data)

#calculate TPC parameters
high.TCP.res <- calc_params(high.fit) %>%
  mutate_all(round, 2)   # round for easy viewing

high.TCP.res 

```

### Bootstrapping high curve fit   

Resampling the original data with replacement
```{r}
# refit model using nlsLM
high.fit_nlsLM <- minpack.lm::nlsLM(rate~sharpeschoolhigh_1981(temp = temp, r_tref,e,eh,th, tref = 28),
                        data = d.high,
                        start = coef(high.fit),
                        lower = low_lims,
                        upper = upper_lims,
                        weights = rep(1, times = nrow(d.high)))

# bootstrap using case resampling
high.boot1 <- Boot(high.fit_nlsLM, method = 'case')

# look at the data
head(high.boot1$t)

# create predictions of each bootstrapped model
high.boot1_preds <- high.boot1$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = 1:n()) %>%
  group_by_all() %>%
  do(data.frame(temp = seq(min(d.high$temp), max(d.high$temp), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = sharpeschoolhigh_1981(temp, r_tref, e, eh, th, tref = 28))

# calculate bootstrapped confidence intervals
high.boot1_conf_preds <- group_by(high.boot1_preds, temp) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

# plot bootstrapped CIs
high.CI.plot <- ggplot() +
  geom_line(aes(temp, .fitted), high.preds, col = "#E9A33D") +
  geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), high.boot1_conf_preds, fill = '#E9A33D', alpha = 0.3) +
  geom_point(aes(temp, rate), d.high, size = 2, alpha = 0.5,col = "#E9A33D") +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration Rate (nmol O2/larva/min')
high.CI.plot

```

```{r}
 #set plot colors
cols <- c("ambient"="#3450A3", "high"="#E9A33D")
  
# plot data and model fit
TPC.plot <- ggplot(data=PRdata, aes(x=temp)) +
   geom_point(aes(temp, rate, color="ambient"), d.amb, size = 2, alpha = 0.5) +
   geom_point(aes(temp, rate, color="high"), d.high, size = 2, alpha = 0.5) +
   geom_line(aes(temp, .fitted), amb.preds, col = '#3450A3', size=2) +
   geom_line(aes(temp, .fitted), high.preds, col = "#E9A33D", size=2) +
   geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), high.boot1_conf_preds, fill = "#E9A33D", alpha = 0.3) +
   geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), amb.boot1_conf_preds, fill = '#3450A3', alpha = 0.3) +
   xlim(21,33)+
   scale_x_continuous(breaks=c(22,24,26,28,30,32,34,36))+
   theme_bw(base_size = 12) +
   scale_colour_manual(name="Treatment",values=cols)+
   theme(legend.position = c(0.55, 0.9),
         panel.border = element_blank(), panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
   labs(x = 'Temperature (ºC)',
        y = expression("Respiration Rate"~nmol~O[2] ~larva^{-1}~min^{-1}))

TPC.plot 

ggsave("Pacu2021/Figures/Respiration/TPC/TPC_SharpSchool.pdf", TPC.plot, dpi=300, w=8, h=8, units="in")

```

### Confidence intervals of TPC parameters   

```{r}
broom::tidy(amb.fit_nlsLM)
broom::tidy(high.fit_nlsLM)

#AMBIENT
#calculate all the TPC parameters
amb.extra_params <- calc_params(amb.fit_nlsLM) %>%
  pivot_longer(everything(), names_to =  'param', values_to = 'estimate')

#calculate CIs for all the TPC parameters
amb.ci_extra_params <- Boot(amb.fit_nlsLM, f = function(x){unlist(calc_params(x))}, labels = names(calc_params(amb.fit_nlsLM)), R = 200, method = 'case') %>%
  confint(., method = 'bca') %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'case bootstrap')

#join the parameters and CIs  
amb.ci_extra_params <- left_join(amb.ci_extra_params, amb.extra_params)
amb.ci_extra_params$Treatment <- "Ambient"

#HIGH
#calculate all the TPC parameters
high.extra_params <- calc_params(high.fit_nlsLM) %>%
  pivot_longer(everything(), names_to =  'param', values_to = 'estimate')

#calculate CIs for all the TPC parameters
high.ci_extra_params <- Boot(high.fit_nlsLM, f = function(x){unlist(calc_params(x))}, labels = names(calc_params(high.fit_nlsLM)), R = 200, method = 'case') %>%
  confint(., method = 'bca') %>%
  as.data.frame() %>%
  rename(conf_lower = 1, conf_upper = 2) %>%
  rownames_to_column(., var = 'param') %>%
  mutate(method = 'case bootstrap')
  
#join the parameters and CIs  
high.ci_extra_params <- left_join(high.ci_extra_params, high.extra_params)
high.ci_extra_params$Treatment <- "High"

#Join Ambient and High estimates and CIs
All_params <- rbind(amb.ci_extra_params, high.ci_extra_params)
All_params <- All_params %>% 
 mutate_if(is.numeric, round, 2)

#Plot all of the estimates
estimate.plots <- ggplot(All_params, aes(Treatment, estimate, color=Treatment)) +
  geom_point(size = 2) +
  scale_color_manual(name="Treatment", values=c("#3450A3","#E9A33D"))+
  geom_linerange(aes(ymin = conf_lower, ymax = conf_upper)) +
  theme_bw() +
  facet_wrap(~param, scales = 'free_y') +
  scale_x_discrete('')

estimate.plots

#filter to only the most relavent and well characterized parameters
All_params <- All_params %>% 
  filter(!param=="ctmin") %>%
  filter(!param=="ctmax") %>%
  filter(!param=="skewness") %>%
  filter(!param=="thermal_safety_margin") %>%
  filter(!param=="thermal_tolerance") %>%
  filter(!param=="q10")%>%
  filter(!param=="breadth")
  
#view estimate plots
estimate.plots <- ggplot(All_params, aes(Treatment, estimate, color=Treatment)) +
  geom_point(size = 2) +
  scale_color_manual(name="Treatment", values=c("#3450A3","#E9A33D"))+
  geom_linerange(aes(ymin = conf_lower, ymax = conf_upper)) +
  theme_bw() +
  labs(y = NULL)+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        legend.position = "none",
        strip.background = element_blank(), 
        strip.placement = "outside") +
  facet_wrap(~param, scales = 'free_y', nrow=1, 
             labeller = as_labeller(c(e = "e (Energy)", eh = " eh (Energy)", rmax= "Rmax (~nmol~O[2] ~larva^{-1}~min^{-1})",topt="Topt (Temperature °C)")), strip.position = "left") +
  scale_x_discrete('')

estimate.plots

ggsave("Pacu2021/Figures/Respiration/TPC/TPC_estimates_SharpSchool.pdf", estimate.plots, dpi=300, w=6, h=2, units="in")
``` 


```{r}
#generate a combined figure of TPCs and estimate plots
figure <- ggarrange(TPC.plot , estimate.plots,
                    labels = c("A", "B"),
                    ncol = 1, nrow = 2,
                    heights=c(1,0.5))
figure

ggsave("Pacu2021/Figures/Figure5_TPC_estimates_SharpeSchoolfield.pdf", figure, dpi=300, w=6, h=8, units="in")
ggsave("Pacu2021/Figures/Figure5_TPC_estimates_SharpeSchoolfield.jpg", figure, dpi=300, w=6, h=8, units="in")

``` 


<!-- ### Gaussian curve fitting   -->

<!-- ```{r} -->
<!-- #AMBIENT -->
<!-- amb.gaus.fit <- nls_multstart(rate~gaussian_1987(temp = temp, rmax, topt, a), -->
<!--                         data = d.amb, -->
<!--                         iter = c(4,4,4), -->
<!--                         start_lower = get_start_vals(d.amb$temp, d.amb$rate, model_name = 'gaussian_1987') - 1, -->
<!--                         start_upper = get_start_vals(d.amb$temp, d.amb$rate, model_name = 'gaussian_1987') + 1, -->
<!--                         lower = get_lower_lims(d.amb$temp, d.amb$rate, model_name = 'gaussian_1987'), -->
<!--                         upper = get_upper_lims(d.amb$temp, d.amb$rate, model_name = 'gaussian_1987'), -->
<!--                         supp_errors = 'Y', -->
<!--                         convergence_count = FALSE) -->


<!-- amb.gaus.fit  -->

<!-- # predict new data -->
<!-- amb_new_data <- data.frame(temp = seq(min(d.amb$temp), max(d.amb$temp), 0.5)) -->
<!-- amb.preds <- augment(amb.gaus.fit, newdata = amb_new_data) -->

<!-- amb.TCP.res <- calc_params(amb.gaus.fit) %>% -->
<!--   mutate_all(round, 2)   # round for easy viewing -->
<!-- amb.TCP.res  -->

<!-- amb.gaus.fit_nlsLM <- minpack.lm::nlsLM(rate~gaussian_1987(temp = temp, rmax, topt, a), -->
<!--                         data = d.amb, -->
<!--                         start = coef(amb.gaus.fit), -->
<!--                         lower = get_lower_lims(d.amb$temp, d.amb$rate, model_name = 'gaussian_1987'), -->
<!--                         upper = get_upper_lims(d.amb$temp, d.amb$rate, model_name = 'gaussian_1987'), -->
<!--                         weights = rep(1, times = nrow(d.amb))) -->

<!-- # bootstrap using case resampling -->
<!-- amb.boot1 <- Boot(amb.gaus.fit_nlsLM, method = 'case') -->

<!-- # look at the data -->
<!-- head(amb.boot1$t) -->

<!-- # create predictions of each bootstrapped model -->
<!-- amb.boot1_preds <- amb.boot1$t %>% -->
<!--   as.data.frame() %>% -->
<!--   drop_na() %>% -->
<!--   mutate(iter = 1:n()) %>% -->
<!--   group_by_all() %>% -->
<!--   do(data.frame(temp = seq(min(d.amb$temp), max(d.amb$temp), length.out = 100))) %>% -->
<!--   ungroup() %>% -->
<!--   mutate(pred = gaussian_1987(temp = temp, rmax, topt, a)) -->

<!-- # calculate bootstrapped confidence intervals -->
<!-- amb.boot1_conf_preds <- group_by(amb.boot1_preds, temp) %>% -->
<!--   summarise(conf_lower = quantile(pred, 0.025), -->
<!--             conf_upper = quantile(pred, 0.975)) %>% -->
<!--   ungroup() -->

<!-- # plot bootstrapped CIs -->
<!-- amb.CI.plot <- ggplot() + -->
<!--   geom_line(aes(temp, .fitted), amb.preds, col = 'blue') + -->
<!--   geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), amb.boot1_conf_preds, fill = 'blue', alpha = 0.3) + -->
<!--   geom_point(aes(temp, rate), d.amb, size = 2, alpha = 0.5,col = 'blue') + -->
<!--   theme_bw(base_size = 12) + -->
<!--   labs(x = 'Temperature (ºC)', -->
<!--        y = 'Respiration Rate (nmol O2/larva/min') -->
<!-- amb.CI.plot  -->

<!-- # HIGH -->
<!-- high.gaus.fit <- nls_multstart(rate~gaussian_1987(temp = temp, rmax, topt, a), -->
<!--                         data = d.high, -->
<!--                         iter = c(4,4,4), -->
<!--                         start_lower = get_start_vals(d.high$temp, d.high$rate, model_name = 'gaussian_1987') - 1, -->
<!--                         start_upper = get_start_vals(d.high$temp, d.high$rate, model_name = 'gaussian_1987') + 1, -->
<!--                         lower = get_lower_lims(d.high$temp, d.high$rate, model_name = 'gaussian_1987'), -->
<!--                         upper = get_upper_lims(d.high$temp, d.high$rate, model_name = 'gaussian_1987'), -->
<!--                         supp_errors = 'Y', -->
<!--                         convergence_count = FALSE) -->


<!-- high.gaus.fit  -->

<!-- # predict new data -->
<!-- high_new_data <- data.frame(temp = seq(min(d.high$temp), max(d.high$temp), 0.5)) -->
<!-- high.preds <- augment(high.gaus.fit, newdata = high_new_data) -->

<!-- high.TCP.res <- calc_params(high.gaus.fit) %>% -->
<!--   mutate_all(round, 2)   # round for easy viewing -->
<!-- high.TCP.res  -->

<!-- high.gaus.fit_nlsLM <- minpack.lm::nlsLM(rate~gaussian_1987(temp = temp, rmax, topt, a), -->
<!--                         data = d.high, -->
<!--                         start = coef(high.gaus.fit), -->
<!--                         lower = get_lower_lims(d.high$temp, d.high$rate, model_name = 'gaussian_1987'), -->
<!--                         upper = get_upper_lims(d.high$temp, d.high$rate, model_name = 'gaussian_1987'), -->
<!--                         weights = rep(1, times = nrow(d.high))) -->

<!-- # bootstrap using case resampling -->
<!-- high.boot1 <- Boot(high.gaus.fit_nlsLM, method = 'case') -->

<!-- # look at the data -->
<!-- head(high.boot1$t) -->

<!-- # create predictions of each bootstrapped model -->
<!-- high.boot1_preds <- high.boot1$t %>% -->
<!--   as.data.frame() %>% -->
<!--   drop_na() %>% -->
<!--   mutate(iter = 1:n()) %>% -->
<!--   group_by_all() %>% -->
<!--   do(data.frame(temp = seq(min(d.high$temp), max(d.high$temp), length.out = 100))) %>% -->
<!--   ungroup() %>% -->
<!--   mutate(pred = gaussian_1987(temp = temp, rmax, topt, a)) -->

<!-- # calculate bootstrapped confidence intervals -->
<!-- high.boot1_conf_preds <- group_by(high.boot1_preds, temp) %>% -->
<!--   summarise(conf_lower = quantile(pred, 0.025), -->
<!--             conf_upper = quantile(pred, 0.975)) %>% -->
<!--   ungroup() -->

<!-- # plot bootstrapped CIs -->
<!-- high.CI.plot <- ggplot() + -->
<!--   geom_line(aes(temp, .fitted), high.preds, col = 'red') + -->
<!--   geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), high.boot1_conf_preds, fill = 'red', alpha = 0.3) + -->
<!--   geom_point(aes(temp, rate), d.high, size = 2, alpha = 0.5,col = 'red') + -->
<!--   theme_bw(base_size = 12) + -->
<!--   labs(x = 'Temperature (ºC)', -->
<!--        y = 'Respiration Rate (nmol O2/larva/min') -->
<!-- high.CI.plot  -->

<!-- # plot data and model fit -->
<!-- TPC.plot <- ggplot() + -->
<!--    geom_point(aes(temp, rate), d.amb, size = 2, alpha = 0.5,col = 'blue') + -->
<!--    geom_point(aes(temp, rate), d.high, size = 2, alpha = 0.5,col = 'red') + -->
<!--    geom_line(aes(temp, .fitted), amb.preds, col = 'blue', size=2) + -->
<!--    geom_line(aes(temp, .fitted), high.preds, col = 'red', size=2) + -->
<!--    geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), high.boot1_conf_preds, fill = 'red', alpha = 0.3) + -->
<!--    geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), amb.boot1_conf_preds, fill = 'blue', alpha = 0.3) + -->
<!--    theme_bw(base_size = 12) + -->
<!--    labs(x = 'Temperature (ºC)', -->
<!--         y = 'Metabolic rate') -->

<!-- TPC.plot  -->

<!-- ggsave("Pacu2021/Figures/Respiration/TPC/TPC_Gaussian.pdf", TPC.plot, dpi=300, w=8, h=8, units="in") -->


<!-- amb.TCP.res  -->
<!-- high.TCP.res  -->

<!-- ``` -->

<!-- ### Confidence intervals of Gaussian TPC parameters   -->

<!-- ```{r} -->

<!-- broom::tidy(amb.fit_nlsLM) -->
<!-- broom::tidy(high.fit_nlsLM) -->
<!-- #AMBIENT -->
<!-- amb.extra_params <- calc_params(amb.fit_nlsLM) %>% -->
<!--   pivot_longer(everything(), names_to =  'param', values_to = 'estimate') -->
<!-- amb.ci_extra_params <- Boot(amb.fit_nlsLM, f = function(x){unlist(calc_params(x))}, labels = names(calc_params(amb.fit_nlsLM)), R = 200, method = 'case') %>% -->
<!--   confint(., method = 'bca') %>% -->
<!--   as.data.frame() %>% -->
<!--   rename(conf_lower = 1, conf_upper = 2) %>% -->
<!--   rownames_to_column(., var = 'param') %>% -->
<!--   mutate(method = 'case bootstrap') -->

<!-- amb.ci_extra_params <- left_join(amb.ci_extra_params, amb.extra_params) -->
<!-- amb.ci_extra_params$Treatment <- "Ambient" -->
<!-- # Joining, by = "param" -->
<!-- #HIGH -->
<!-- high.extra_params <- calc_params(high.fit_nlsLM) %>% -->
<!--   pivot_longer(everything(), names_to =  'param', values_to = 'estimate') -->
<!-- high.ci_extra_params <- Boot(high.fit_nlsLM, f = function(x){unlist(calc_params(x))}, labels = names(calc_params(high.fit_nlsLM)), R = 200, method = 'case') %>% -->
<!--   confint(., method = 'bca') %>% -->
<!--   as.data.frame() %>% -->
<!--   rename(conf_lower = 1, conf_upper = 2) %>% -->
<!--   rownames_to_column(., var = 'param') %>% -->
<!--   mutate(method = 'case bootstrap') -->

<!-- high.ci_extra_params <- left_join(high.ci_extra_params, high.extra_params) -->
<!-- high.ci_extra_params$Treatment <- "High" -->
<!-- #Join Ambient and High estimates and CIs -->
<!-- All_params <- rbind(amb.ci_extra_params, high.ci_extra_params) -->
<!-- All_params <- All_params %>%  -->
<!--  mutate_if(is.numeric, round, 2) -->
<!-- #Plot -->
<!-- estimate.plots <- ggplot(All_params, aes(Treatment, estimate, color=Treatment)) + -->
<!--   geom_point(size = 2) + -->
<!--   scale_color_manual(name="Treatment", values=c("blue","red"))+ -->
<!--   geom_linerange(aes(ymin = conf_lower, ymax = conf_upper)) + -->
<!--   theme_bw() + -->
<!--   facet_wrap(~param, scales = 'free_y') + -->
<!--   scale_x_discrete('') -->
<!-- estimate.plots -->
<!-- All_params <- All_params %>%  -->
<!--   filter(!param=="ctmin") %>% -->
<!--   filter(!param=="ctmax") %>% -->
<!--   filter(!param=="skewness") %>% -->
<!--   filter(!param=="thermal_safety_margin") %>% -->
<!--   filter(!param=="thermal_tolerance") %>% -->
<!--   filter(!param=="q10")%>% -->
<!--   filter(!param=="breadth") -->

<!-- estimate.plots <- ggplot(All_params, aes(Treatment, estimate, color=Treatment)) + -->
<!--   geom_point(size = 2) + -->
<!--   scale_color_manual(name="Treatment", values=c("blue","red"))+ -->
<!--   geom_linerange(aes(ymin = conf_lower, ymax = conf_upper)) + -->
<!--   theme_bw() + -->
<!--   labs(y = NULL)+ -->
<!--   theme(axis.title.x=element_blank(), -->
<!--         axis.text.x=element_blank(), -->
<!--         legend.position = "none", -->
<!--         strip.background = element_blank(),  -->
<!--         strip.placement = "outside") + -->
<!--   facet_wrap(~param, scales = 'free_y', nrow=1,  -->
<!--              labeller = as_labeller(c(e = "e (Energy)", eh = " eh (Energy)", rmax= "Rmax (~nmol~O[2] ~larva^{-1}~min^{-1})",topt="Topt (Temperature °C)")), strip.position = "left") + -->
<!--   scale_x_discrete('') -->
<!-- estimate.plots -->
<!-- ggsave("Pacu2021/Figures/Respiration/TPC/TPC_estimates.pdf", estimate.plots, dpi=300, w=6, h=2, units="in") -->
<!-- ```  -->


<!-- ```{r} -->
<!-- figure <- ggarrange(TPC.plot , estimate.plots, -->
<!--                     labels = c("A", "B"), -->
<!--                     ncol = 1, nrow = 2, -->
<!--                     heights=c(1,0.5)) -->
<!-- figure -->
<!-- ggsave("Pacu2021/Figures/FigureX_TPC_estimates_Gaussian.pdf", figure, dpi=300, w=6, h=8, units="in") -->
<!-- ggsave("Pacu2021/Figures/FigureX_TPC_estimates_Gaussian.jpg", figure, dpi=300, w=6, h=8, units="in") -->
<!-- ``` -->