---
title: "Photosynthesis TPC fitting by Colony"
authors: Hollie Putnam 
edited by: Hollie Putnam 
date: 20230829
output: html_document
---

Load libraries
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(rTPC)
library(nls.multstart)
library(broom)
library(tidyverse)
```

## Import data
```{r, warning = FALSE}
Photodata <- read.csv("data/Dec_Photo_Rawextracted_rates.csv")
Photodata$temp <- as.numeric(Photodata$Temp.Cat)
Photodata <- Photodata %>%
  filter(Temp.Cat!=22)
Photodata$rate <- log10(Photodata$micromol.cm2.h+1)
```

TPC fitting 
Padifeld et al **rTPC and nls.multstart: A new pipeline to fit thermal performance curves in r**  
https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/2041-210X.13585  

Sharpe Schoolfield 1981 model
Schoolfield, R. M., Sharpe, P. J. H., & Magnuson, C. E. (1981). Non-linear regression of biological temperature-dependent rate models based on absolute reaction-rate theory. Journal of theoretical biology, 88(4), 719-731. https://doi.org/10.1016/0022-5193(81)90246-0

# ```{r}
# # choose model
# get_model_names()
# #sharpeschoolhigh_1981
# 
# # get start vals
# start_vals <- get_start_vals(Photodata$temp,Photodata$transformed.rate, model_name = 'sharpeschoolhigh_1981')
# 
# # get limits
# low_lims <- get_lower_lims(Photodata$temp,Photodata$transformed.rate, model_name = 'sharpeschoolhigh_1981')
# upper_lims <- get_upper_lims(Photodata$temp,Photodata$transformed.rate, model_name = 'sharpeschoolhigh_1981')
# 
# #view values
# start_vals
# start_vals <- start_vals %>% replace(is.na(.), 0)
# start_vals
# low_lims
# upper_lims
# ```

#Individual curve fits test
```{r}
# grandis CURVE FIT
d.grandis.dec <- Photodata %>% 
  filter(fragment_ID == "POC-156")

plot1 <- ggplot() +
  geom_point(aes(temp, rate), d.grandis.dec, size = 2, alpha = 0.5,col = 'brown') +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Log 10 +1 Rate (µmol O2/cm2/h)')
plot1

```

#Individual curve fits December
```{r}

d <- Photodata

# when scaling up our code to fit hundreds of models, its nice to have a progress bar
# edit nls_multstart to allow for a progress bar
nls_multstart_progress <- function(formula, data = parent.frame(), iter, start_lower, 
                                   start_upper, supp_errors = c("Y", "N"), convergence_count = 100, 
                                   control, modelweights, ...){
  if(!is.null(pb)){
    pb$tick()
  }
  nls_multstart(formula = formula, data = data, iter = iter, start_lower = start_lower, 
                start_upper = start_upper, supp_errors = supp_errors, convergence_count = convergence_count, 
                control = control, modelweights = modelweights, ...)
}

# start progress bar and estimate time it will take
number_of_models <- 2
number_of_curves <- length(unique(d$Number))

# setup progress bar
pb <- progress::progress_bar$new(total = number_of_curves*number_of_models,
                                 clear = FALSE,
                                 format ="[:bar] :percent :elapsedfull")




# fit two chosen model formulation in rTPC
d_fits <- nest(d, data = c(temp, rate)) %>%
  mutate(gaussian = map(data, ~nls_multstart_progress(rate~gaussian_1987(temp = temp, rmax,topt,a),
                        data = .x,
                        iter = c(3,3,3),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'gaussian_1987') - 1,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'gaussian_1987') + 1,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'gaussian_1987'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'gaussian_1987'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)),
         sharpeschoolhigh = map(data, ~nls_multstart_progress(rate~sharpeschoolhigh_1981(temp = temp, r_tref,e,eh,th, tref = 15),
                        data = .x,
                        iter = c(3,3,3,3),
                        start_lower = get_start_vals(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981') - 1,
                        start_upper = get_start_vals(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981') + 1,
                        lower = get_lower_lims(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981'),
                        upper = get_upper_lims(.x$temp, .x$rate, model_name = 'sharpeschoolhigh_1981'),
                        supp_errors = 'Y',
                        convergence_count = FALSE)))

```


